### 2021-01-13 about/vita.tex
Updated vita

\font\eightrm=cmr8
\font\elevensc=cmcsc11  % For section headers
\font\bigbold=cmb12  % Name
\font\tenb=cmb10
\font\mc=cmr9

@@

\def\up#1{\leavevmode \raise.16ex\hbox{#1}}
\def\sectheader#1{{\bigskip\elevensc #1}\smallskip\hrule\medskip}
\def\leftright#1#2{{#1}\hfill{#2}\par}
\def\myname{{\tensc Marcel K. Goh}}
\def\CEE{{\mc C}}
\def\UNIX{{\mc UNIX}}
\def\thing{\item{$\bullet$}}

@@

\leftright{\bigbold Marcel K.\ Goh}{3660 Rue Hutchison, Apt.\ 4}
\leftright{Email: marcel\_goh@yahoo.ca}{Montr\'eal, QC H2X 2H3, Canada}
\leftright{URL: marcelgoh.github.io}{+1\thinspace\up(825\up)\thinspace 440-0681}

@@

\leftright{\bf McGill University}{\bf September 2017 -- April 2021}
\leftright{\sl BSc, Honours Mathematics and Computer Science, minor Linguistics}{\sl Montr\'eal, QC, Canada}
CGPA: 3.81/4.
\medbreak
\leftright{\bf Charles University}{\bf February -- June 2019}
\leftright{\sl Exchange semester, Faculty of Mathematics and Physics}{\sl Prague, Czech Republic}
Grade: 1 on all courses (highest score attainable).

@@

\leftright{\bf Department of Mathematics and Statistics, McGill University}{\bf September 2019 -- present}
\leftright{\sl Student Grader}{\sl Montr\'eal, QC, Canada}
\smallskip
Grading of assignments in the following courses:
\begingroup\parindent=10pt
\smallskip
\thing Fall 2020: MATH 323 Probability, MATH 456 Honours Algebra 3
\smallskip
\thing Winter 2020: MATH 240 Discrete Structures
\smallskip
\thing Fall 2019: MATH 235 Algebra 1
\endgroup
\medbreak

@@

\parindent=10pt
\thing Scored 10/120 on the William Lowell Putnam Mathematical Competition in 2019
(the median score that year was 2/120).
\smallskip
\thing Recipient of 0x\$3.40 in Knuth reward cheques.
\medbreak

>>>>

\font\eightrm=cmr8
\font\elevensc=cmcsc11  % For section headers
\font\bigbold=cmb10 at 12pt  % Name
\font\tenb=cmb10
\font\mc=cmr9

@@

\def\up#1{\leavevmode \raise.16ex\hbox{#1}}
\def\sectheader#1{{\bigskip\elevensc #1}\smallskip\hrule\medskip}
\def\leftright#1#2{{#1}\hfill{#2}\par}
\def\CEE{{\mc C}}
\def\UNIX{{\mc UNIX}}
\def\thing{\item{$\bullet$}}

@@

\leftright{\bigbold Marcel K.\ Goh
\ifx\Umathchar\undefined\else% Chinese characters do not appear when using pdfTeX
\font\chinese="STKaiti" at 12pt%
\font\twelverm=cmr12%
\twelverm\up({\chinese 吳麒仁}\up)%
\fi}{3660 Rue Hutchison, Apt.\ 4}
\leftright{Email: marcel\_goh@yahoo.ca}{Montr\'eal, QC H2X 2H3, Canada}
\leftright{URL: marcelgoh.github.io}{+1\thinspace\up(825\up)\thinspace 440-0681}

@@

\leftright{\bf McGill University}{\bf September 2017 -- April 2021}
\leftright{\sl BSc, Honours Mathematics and Computer Science, minor Linguistics}{\sl Montr\'eal, QC, Canada}
CGPA: 3.82/4.
\medbreak
\leftright{\bf Charles University}{\bf February -- June 2019}
\leftright{\sl Exchange semester, Faculty of Mathematics and Physics}{\sl Prague, Czech Republic}
Grade: 1 on all courses (highest score attainable).

@@

\leftright{\bf Department of Mathematics and Statistics, McGill University}{\bf September 2019 -- present}
\leftright{\sl Student Grader}{\sl Montr\'eal, QC, Canada}
\smallskip
Grading of assignments in the following courses:
\begingroup\parindent=10pt
\smallskip
\thing Winter 2021: MATH 457 Honours Algebra 4
\smallskip
\thing Fall 2020: MATH 323 Probability, MATH 456 Honours Algebra 3
\smallskip
\thing Winter 2020: MATH 240 Discrete Structures
\smallskip
\thing Fall 2019: MATH 235 Algebra 1
\endgroup
\medbreak

@@

\parindent=10pt
\thing Scored 10/120 on the William Lowell Putnam Mathematical Competition in 2019
(the median score that year was 2/120).
\smallskip
\thing Recipient of 0x\$3.40 in Knuth reward cheques.
\smallskip
\thing Contributed sequences A335562, A338550, and A338993 to the On-line Encyclopedia of Integer Sequences.
\medbreak
